---
title: "Clean code for all lakes"
format: html
editor: visual
---

## 1. Data for response diversity

```{r}
#| eval: false
#rm(list = ls())
#removes all variables from the current environment, not necessary for what I am doing here
library(tidyverse)
library(patchwork)
library(ggtext)
library(mgcv)
library(gratia)
#library(hypervolume)
library(here)
library(readr)

# function from Ross et al. and species colors are now seperate
source(here("functions.R"))
source(here("species_colors.R"))

# load final dataset
df_final_no_electro <- read_rds("/home/sophie/Dokumente/Master Thesis R/Master Thesis Analysis/df_final_ne.rds")

```

## 1.5 Small lakes for testing

```{r}
#now checking all summaries, try to add summary of gam to code
#working
#next: how can I interpret the summary?
#repeat interpretation for all species in all lakes in abundance and presence/absence

#gam.check cant be stored as a RDS file

# change that presence and abundance are in one column with one column for value
nets_df_final <- df_final_no_electro |> 
  pivot_longer(
    cols = c("Abundance", "Presence"), 
    names_to = "Parameter", 
    values_to = "value"
  )

abu_nets_df_final <- nets_df_final |> 
  filter(Parameter == "Abundance")

df_small <- abu_nets_df_final |>
  filter(Lake %in% c("Biel", "Brienz", "Walen"))

small_lakes <- df_small |>
  distinct(Lake) |>
  pull(Lake)


# make empty lists for the new data provided by the loop
gam_output <- list()
model_prediction <- list()
derivatives <- list()



#how can I store the summary outputs for all species?? sink() works with append
#loop for all lakes

for (i in small_lakes){
  presence_lake <- df_small |>
    filter(Lake == i)
  species_list <- presence_lake |>
    distinct(Species) |>
    pull(Species)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(presence_lake$mean_last_7days, na.rm = TRUE), to = max(presence_lake$mean_last_7days, na.rm = TRUE), by = 0.02))
  #saveRDS(species_list,paste0("test_species/species_", i,".rds"))
  for (j in species_list){ #looping through all species occuring in this lake
    data <- presence_lake |> 
      filter(Species == j)
    gam_output[[j]] <- gam(data = data, value ~ s(mean_last_7days, k = 3, bs = "cs"), family = negbin(1), method = "REML") #GAM per species in all lakes
    # summary <- summary(gam_output[[j]])
    # sink("gam_summary_small.txt", append = TRUE)
    # print(summary)
    # sink()
    #summary or summary.gam? kommt aufs gleiche, also egal
    summary <- summary.gam(gam_output[[j]])
    sink("summary_gam_test.txt", append = TRUE)
    print.summary.gam(summary)
    sink()
    #saveRDS(summary, paste0("test_summary/summary_",i,"_", j,".rds"))
    model_prediction[[j]] <- predict.gam(gam_output[[j]], temp_gradient, type = "response", se.fit = TRUE)$fit #saving model predictions in RDS
    model_bind <- cbind(model_prediction[[j]], temp_gradient)
    saveRDS(model_bind, paste0("test_predictions_abu_small/predictions_",i,"_",j,".rds"))
    derivatives[[j]] <- derivatives(gam_output[[j]]) #making derivatives and saving them in a RDS
    saveRDS(derivatives[[j]], paste0("test_deriv_abu_small/derivatives_",i,"_",j,".rds"))
  }

}


# test <- readRDS("test_summary/summary_Biel_Abramis_brama.rds")
# test4 <- readRDS("test_summary/summary_Biel_Cobitis_bilineata.rds")
# test2 <- readRDS("test_summary/summaryBiel_Perca_fluviatilis.rds")
# test3 <- readRDS("test_summary/summaryWalen_Coregonus_sp.rds")
```

```{r}

#preparing dfs with predictions for all lakes

path_pred <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/test_predictions_abu_small"

predictions_list <-list.files(path_pred)

predictions_lakes <- list()

#loop works!!!!!!! first real loop of my life
for (i in small_lakes){
  predictions_lakes <- predictions_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  pred <- list()
  lake_data <- df_small |>
    filter(Lake == i)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(lake_data$mean_last_7days, na.rm = TRUE), to = max(lake_data$mean_last_7days, na.rm = TRUE), by = 0.02)) #add temperature gradient to add to the df
  for (j in predictions_lakes){
    # print(predictions_test)
    pred[[j]] <- readRDS(paste0(path_pred,"/", j))
    df_pred <- pred |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(model_prediction = `model_prediction[[j]]`) |> #does not work
      rename(temp = mean_last_7days) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_pred, paste0("test_df_pred/df_pred_", i, ".rds"))
      
  }
}

# derivatives
path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/test_deriv_abu_small"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in small_lakes){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_deriv, paste0("test_df_deriv/df_deriv_", i, ".rds"))
  }
}

# test <- readRDS("df_derivatives/df_deriv_Biel.rds")
#response diversity

path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/test_deriv_abu_small"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in small_lakes){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data)
    df_resp_div <- df_deriv |> 
      select(Species, temp, derivative) |> 
      pivot_wider(
        names_from = Species,
        values_from = derivative) |> 
      rename_all(~stringr::str_replace(.,"^derivatives_","")) |> 
      rename_all(~stringr::str_replace(.,"^[^_]*_", "")) |>
      rename_with(~ sub(".rds$", "", .x), everything())
    #test <- df_resp_div |>
      #select (-temp) |>
      #mutate_all(rdiv = resp_div(1, sign_sens = F))
    df_resp_div$rdiv <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = F)
    df_resp_div$sign <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = T)
    df_resp_div$Med <- median(df_resp_div$rdiv)
    saveRDS(df_resp_div, paste0("test_df_resp/df_resp_div_", i, ".rds"))
  }
}


```

```{r}
df_walen_resp_div <- readRDS("test_df_resp/df_resp_div_Walen.rds")

fig_c <- ggplot(data = df_walen_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_walen_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_c

# fig_d <- ggplot(data = df_walen_resp_div, mapping = aes(x = temp, y = sign)) +
#   theme_classic(base_size = 14) +
#   labs(x = "Temperature", y = "Sign", tag = "d)") +
#   geom_line()




```

## 2. Abundance: Calculating Response Diversity for all lakes

```{r}
#| eval: false
rm(list = ls())
#removes all variables from the current environment, not necessary for what I am doing here
library(tidyverse)
library(patchwork)
library(ggtext)
library(mgcv)
library(gratia)
#library(hypervolume)
library(here)
library(readr)

# function from Ross et al. and species colors are now seperate
source(here("functions.R"))
source(here("species_colors.R"))

# load final dataset
df_final_no_electro <- read_rds("/home/sophie/Dokumente/Master Thesis R/Master Thesis Analysis/df_final_ne.rds")
```

### Preparing predictions and derivatives

First trying it with nested data. Otherwise, doing a for loop or a function

```{r}
# df_final_ne does not include the data from electro fishing -> different number of fish species per lake

# change that presence and abundance are in one column with one column for value
nets_df_final <- df_final_no_electro |> 
  pivot_longer(
    cols = c("Abundance", "Presence"), 
    names_to = "Parameter", 
    values_to = "value"
  )


# make list of all lakes
lakes_list <- nets_df_final |> 
  distinct(Lake) |> 
  pull(Lake)
# working with an abundance subset of this dataset
# if else statement in loop would be a possibility
abu_nets_df_final <- nets_df_final |> 
  filter(Parameter == "Abundance")

# make temperature gradient for the prediction
# temp_gradient <- data.frame(mean_last_7days = seq(from = min(abu_nets_df_final$mean_last_7days, na.rm = TRUE), to = max(abu_nets_df_final$mean_last_7days, na.rm = TRUE), by = 0.02))


# make empty lists for the new data provided by the loop
gam_output <- list()
model_prediction <- list()
derivatives <- list()


#loop for all lakes
#to get summary.txt only, dont run code below sink()

for (i in lakes_list){
  presence_lake <- abu_nets_df_final |>
    filter(Lake == i)
  species_list <- presence_lake |>
    distinct(Species) |>
    pull(Species)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(presence_lake$mean_last_7days, na.rm = TRUE), to = max(presence_lake$mean_last_7days, na.rm = TRUE), by = 0.02))
  #saveRDS(species_list,paste0("test_species/species_", i,".rds"))
  for (j in species_list){ #looping through all species occuring in this lake
    data <- presence_lake |> 
      filter(Species == j)
    gam_output[[j]] <- gam(data = data, value ~ s(mean_last_7days, k = 3, bs = "cs"), family = negbin(1), method = "REML") #GAM per species in all lakes
    summary <- summary.gam(gam_output[[j]]) #txt file prepared with all summaries 
    sink("summary_gams_abundance_temp.txt", append = TRUE)
    print.summary.gam(summary)
    sink()
    model_prediction[[j]] <- predict.gam(gam_output[[j]], temp_gradient, type = "response", se.fit = TRUE)$fit #saving model predictions in RDS
    model_bind <- cbind(model_prediction[[j]], temp_gradient)
    saveRDS(model_bind, paste0("predictions_abundance/predictions_",i,"_",j,".rds"))
    derivatives[[j]] <- derivatives(gam_output[[j]]) #making derivatives and saving them in a RDS
    saveRDS(derivatives[[j]], paste0("derivatives_abundance/derivatives_",i,"_",j,".rds"))
  }

}

# freiwillig
#is there a faster way to generate the df for lake plotting?
```

### DFs loops

```{r}
#preparing dfs with predictions for all lakes

path_pred <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/predictions_abundance"

predictions_list <-list.files(path_pred)

predictions_lakes <- list()

#loop works!!!!!!! first real loop of my life
for (i in lakes_list){
  predictions_lakes <- predictions_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  pred <- list()
  lake_data <- abu_nets_df_final |>
    filter(Lake == i)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(lake_data$mean_last_7days, na.rm = TRUE), to = max(lake_data$mean_last_7days, na.rm = TRUE), by = 0.02)) #add temperature gradient to add to the df
  for (j in predictions_lakes){
    # print(predictions_test)
    pred[[j]] <- readRDS(paste0(path_pred,"/", j))
    df_pred <- pred |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(model_prediction = `model_prediction[[j]]`) |> #does not work
      rename(temp = mean_last_7days) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_pred, paste0("df_predictions/df_pred_", i, ".rds"))
      
  }
}

# derivatives
path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/derivatives_abundance"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in lakes_list){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_deriv, paste0("df_derivatives/df_deriv_", i, ".rds"))
  }
}

test <- readRDS("df_derivatives/df_deriv_Biel.rds")
#response diversity

path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/derivatives_abundance"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in lakes_list){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data)
    df_resp_div <- df_deriv |> 
      select(Species, temp, derivative) |> 
      pivot_wider(
        names_from = Species,
        values_from = derivative) |> 
      rename_all(~stringr::str_replace(.,"^derivatives_","")) |> 
      rename_all(~stringr::str_replace(.,"^[^_]*_", "")) |>
      rename_with(~ sub(".rds$", "", .x), everything())
    #test <- df_resp_div |>
      #select (-temp) |>
      #mutate_all(rdiv = resp_div(1, sign_sens = F))
    df_resp_div$rdiv <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = F)
    df_resp_div$sign <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = T)
    df_resp_div$Med <- median(df_resp_div$rdiv)
    saveRDS(df_resp_div, paste0("df_response_diversity/df_resp_div_", i, ".rds"))
  }
}


###TO DO #####
#1. remove lake names in front of species names in predictions: done
#2. remove blabla around species name in derivatives in column: done
#3. find easy way to calculate response diversity: done

##Fakultative ###
#response diversity kürze
```

# !!!Testing problems of Temperature in df_pred

```{r}
# 
# #small lake subset to try loop
# 
# 
# gam_output <- list()
# model_prediction <- list()
# 
# derivatives <- list()
# 
# df_small <- abu_nets_df_final |>
#   filter(Lake %in% c("Biel", "Brienz", "Walen"))
# 
# small_lakes <- df_small |>
#   distinct(Lake) |>
#   pull(Lake)
# 
# #neue änderung: cbind of model_prediction and temp_gradient and then save this as RDS
# for (i in small_lakes){
#   presence_lake <- df_small |>
#     filter(Lake == i)
#   species_list <- presence_lake |>
#     distinct(Species) |>
#     pull(Species)
#   temp_gradient <- data.frame(mean_last_7days = seq(from = min(presence_lake$mean_last_7days, na.rm = TRUE), to = max(presence_lake$mean_last_7days, na.rm = TRUE), by = 0.02))
#   for (j in species_list){ #looping through all species occuring in this lake
#     data <- presence_lake |>
#       filter(Species == j)
#     gam_output[[j]] <- gam(data = data, value ~ s(mean_last_7days, k = 3, bs = "cs"), family = negbin(1), method = "REML") #GAM per species in all lakes
#     model_prediction[[j]] <- predict.gam(gam_output[[j]], temp_gradient, type = "response", se.fit = TRUE)$fit #saving model predictions in RDS
#     test_bind <- cbind(model_prediction[[j]], temp_gradient)
#     saveRDS(test_bind, paste0("aa_pred_test/predictions_",i,"_",j,".rds"))
#     derivatives[[j]] <- derivatives(gam_output[[j]]) #making derivatives and saving them in a RDS
#     # saveRDS(derivatives[[j]], paste0("aa_deriv_test/derivatives_",i,"_",j,".rds"))
#     }
# }
# 
# #testing if bind works to get the temperature data too
# test_pred <- readRDS("aa_pred_test/predictions_Biel_Abramis_brama.rds")
# #now temperature gradient present
# # loop for df_pred
# 
# path_pred <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/aa_pred_test"
# 
# predictions_list <-list.files(path_pred)
# 
# predictions_lakes <- list()
# 
# #loop works!!!!!!! first real loop of my life
# for (i in small_lakes){
#   predictions_lakes <- predictions_list |> 
#     as_tibble() |> 
#     filter(str_detect(value, i)) |> 
#     pull(value)
#   pred <- list()
#   lake_data <- abu_nets_df_final |>
#     filter(Lake == i)
#   # temp_gradient <- data.frame(mean_last_7days = seq(from = min(lake_data$mean_last_7days, na.rm = TRUE), to = max(lake_data$mean_last_7days, na.rm = TRUE), by = 0.02)) 
#   for (j in predictions_lakes){
#     # print(predictions_test)
#     pred[[j]] <- readRDS(paste0(path_pred,"/", j))
#     # df_new <- pred |>
#     #   bind_cols() |> 
#     #   rename_all(~stringr::str_replace(.,"^predictions_","")) |>
#     #   rename_all(~stringr::str_replace(.,"^[^_]*_", "")) |> #lake is also subsetted
#     #   rename_with(~ sub(".rds$", "", .x), everything())
#     df_test <- pred |>
#       bind_rows(.id ="id") |>
#       rename(Species = id) |> 
#       rename(model_prediction = `model_prediction[[j]]`) |> #does not work
#       rename(temp = mean_last_7days) |> 
#       mutate(Species = sub("^[^_]*_", "", Species)) |> 
#       mutate(Species = sub("^[^_]*_", "", Species)) |>
#       mutate(Species = sub("\\.rds$", "", Species))
#     # df_pred <- df_new |>
#     #   pivot_longer(
#     #     cols = everything(),
#     #     names_to = "Species",
#     #     values_to = "model_prediction")
#     saveRDS(df_test, paste0("aa_test/df_pred_", i, ".rds"))
#   }
# }
# 
# test_pred <- readRDS("aa_pred_test/predictions_Biel_Abramis_brama.rds")
# deriv_test <- readRDS("derivatives_abundance/derivatives_Biel_Abramis_brama.rds")
# 
# ###problem: in derivatives a tibble is made, in predictions it is just values (array), we need a tibble
# test <- readRDS("aa_test/df_pred_Biel.rds")
# test2 <- readRDS("aa_test/df_pred_Brienz.rds")
# 
# test_new <- test2 |> 
#   rename(model_prediction = `model_prediction[[j]]`)
# 
# walen <- readRDS("aa_test/df_pred_Walen.rds")
# #solved
# #to do
# #1. check if the tibble is the same as with the former code: done
# #2. change name of model_prediction column: done
# #3. change code for all species
# 
# fig_a <- ggplot() +
#   theme_classic(base_size = 14) +
#   labs(x = "Temperature", y = "Abundance", tag = "a)") +
#   geom_hline(
#     yintercept = 0,
#     lty = 2) +
#   geom_line(data = test, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
#   scale_colour_manual(values = lakeColors, guide = NULL)
# 
# fig_a

```

## 3. Presence

Deleting everything to reduce possibility of errors

```{r}
#| eval: false
rm(list = ls())
#removes all variables from the current environment, not necessary for what I am doing here
library(tidyverse)
library(patchwork)
library(ggtext)
library(mgcv)
library(gratia)
#library(hypervolume)
library(here)
library(readr)

# function includes lakeColors
source(here("functions.R"))
source(here("species_colors.R"))

# load final dataset
df_final_no_electro <- read_rds("/home/sophie/Dokumente/Master Thesis R/Master Thesis Analysis/df_final_ne.rds")

```

```{r}
# df_final_ne does not include the data from electro fishing -> different number of fish species per lake

# change that presence and abundance are in one column with one column for value
nets_df_final <- df_final_no_electro |> 
  pivot_longer(
    cols = c("Abundance", "Presence"), 
    names_to = "Parameter", 
    values_to = "value"
  )


# make list of all lakes
lakes_list <- nets_df_final |> 
  distinct(Lake) |> 
  pull(Lake)


# working with a presence subset of this dataset
pre_nets_df_final <- nets_df_final |> 
  filter(Parameter == "Presence")

# make temperature gradient for the prediction
# temp_gradient <- data.frame(mean_last_7days = seq(from = min(abu_nets_df_final$mean_last_7days, na.rm = TRUE), to = max(abu_nets_df_final$mean_last_7days, na.rm = TRUE), by = 0.02))


# make empty lists for the new data provided by the loop
gam_output <- list()
model_prediction <- list()
derivatives <- list()


#loop for all lakes

for (i in lakes_list){
  presence_lake <- pre_nets_df_final |>
    filter(Lake == i)
  species_list <- presence_lake |>
    distinct(Species) |>
    pull(Species)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(presence_lake$mean_last_7days, na.rm = TRUE), to = max(presence_lake$mean_last_7days, na.rm = TRUE), by = 0.02))
  #saveRDS(species_list,paste0("test_species/species_", i,".rds"))
  for (j in species_list){ #looping through all species occuring in this lake
    data <- presence_lake |> 
      filter(Species == j)
    gam_output[[j]] <- gam(data = data, value ~ s(mean_last_7days, k = 3, bs = "cs"), family = binomial, method = "REML") #GAM per species in all lakes
    summary <- summary.gam(gam_output[[j]]) #txt file prepared with all summaries 
    sink("summary_gams_presence_temp.txt", append = TRUE)
    print.summary.gam(summary)
    sink()
    #model_prediction[[j]] <- predict.gam(gam_output[[j]], temp_gradient, type = "response", se.fit = TRUE)$fit #saving model predictions in RDS
    #model_bind <- cbind(model_prediction[[j]], temp_gradient)
    #saveRDS(model_bind, paste0("predictions_presence/predictions_",i,"_",j,".rds"))
    #derivatives[[j]] <- derivatives(gam_output[[j]]) #making derivatives and saving them in a RDS
    #saveRDS(derivatives[[j]], paste0("derivatives_presence/derivatives_",i,"_",j,".rds"))
  }

}

# freiwillig
#is there a faster way to generate the df for lake plotting?
```

```{r}
#preparing dfs with predictions for all lakes

path_pred <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/predictions_presence"

predictions_list <-list.files(path_pred)

predictions_lakes <- list()

#loop works!!!!!!! first real loop of my life
for (i in lakes_list){
  predictions_lakes <- predictions_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  pred <- list()
  lake_data <- pre_nets_df_final |>
    filter(Lake == i)
  temp_gradient <- data.frame(mean_last_7days = seq(from = min(lake_data$mean_last_7days, na.rm = TRUE), to = max(lake_data$mean_last_7days, na.rm = TRUE), by = 0.02)) #add temperature gradient to add to the df
  for (j in predictions_lakes){
    # print(predictions_test)
    pred[[j]] <- readRDS(paste0(path_pred,"/", j))
    df_pred <- pred |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(model_prediction = `model_prediction[[j]]`) |> #does not work
      rename(temp = mean_last_7days) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_pred, paste0("df_predictions_presence/df_pred_", i, ".rds"))
  }
}


# derivatives
path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/derivatives_presence"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in lakes_list){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |> 
      mutate(Species = sub("^[^_]*_", "", Species)) |>
      mutate(Species = sub("\\.rds$", "", Species))
    saveRDS(df_deriv, paste0("df_derivatives_presence/df_deriv_", i, ".rds"))
  }
}


#response diversity

path_deriv <- "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/derivatives_presence"

deriv_list <-list.files(path_deriv)

deriv_lakes <- list()

for (i in lakes_list){
  deriv_lakes <- deriv_list |> 
    as_tibble() |> 
    filter(str_detect(value, i)) |> 
    pull(value)
  deriv <- list()
  for (j in deriv_lakes){
    # print(predictions_test)
    deriv[[j]] <- readRDS(paste0(path_deriv,"/", j))
    df_deriv <- deriv |>
      bind_rows(.id ="id") |>
      rename(Species = id) |> 
      rename(temp = data)
    df_resp_div <- df_deriv |> 
      select(Species, temp, derivative) |> 
      pivot_wider(
        names_from = Species,
        values_from = derivative) |> 
      rename_all(~stringr::str_replace(.,"^derivatives_","")) |> 
      rename_all(~stringr::str_replace(.,"^[^_]*_", "")) |> 
      rename_with(~ sub(".rds$", "", .x), everything())
    df_resp_div$rdiv <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = F)
    df_resp_div$sign <- apply(df_resp_div[,-1, drop = FALSE], 1, resp_div, sign_sens = T)
    df_resp_div$Med <- median(df_resp_div$rdiv)
    saveRDS(df_resp_div, paste0("df_response_diversity_presence/df_resp_div_", i, ".rds"))
  }
}

#should it be -2?
```

## 4. Plotting part

```{r}
#| eval: false
# rm(list = ls())
#removes all variables from the current environment, not necessary for what I am doing here
library(tidyverse)
library(patchwork)
library(ggtext)
library(mgcv)
library(gratia)
#library(hypervolume)
library(here)
library(readr)

# function includes lakeColors
source(here("functions.R"))
source(here("species_colors.R"))

```

### Loading DFs

```{r}
#loading all dfs
#predictions
# file_path <-  "/home/sophie/Dokumente/Master Thesis R/response-diversity-in-swiss-lakes/df_predictions"
# 
# file_list <-list.files(file_path)
# liste_predictions <- list()
# 
# for (i in lakes_list){
#   liste_predictions <- file_list |> 
#     as_tibble() |> 
#     filter(str_detect(value, i)) |> 
#     pull(value)
#   for (j in liste_predictions){
#     
#     
#   }
# }

```

## Plots

Testing

```{r}
# df_walen_pred <- readRDS("df_predictions/df_pred_Walen.rds")
df_walen_pred_pres <- readRDS("df_predictions_presence/df_pred_Walen.rds")
# df_walen_deriv <- readRDS("df_derivatives/df_deriv_Walen.rds")
df_walen_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Walen.rds")
# df_walen_resp_div <- readRDS("df_response_diversity/df_resp_div_Walen.rds")
df_walen_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Walen.rds")
```

#### Biel

```{r}

#not working because of species names!!
df_biel_pred <- readRDS("df_predictions/df_pred_Biel.rds")
df_biel_pred_pres <- readRDS("df_predictions_presence/df_pred_Biel.rds")
df_biel_deriv <- readRDS("df_derivatives/df_deriv_Biel.rds")
df_biel_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Biel.rds")
df_biel_resp_div <- readRDS("df_response_diversity/df_resp_div_Biel.rds")
df_biel_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Biel.rds")

##plotting test biel
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_biel_pred, mapping = aes(x = temp, y = model_prediction, color = Species)) +
  scale_colour_manual(values = lakeColors, guide = NULL)
  # lims(y = c(ymin_p, ymax_p))

# fig_a

fig_b <- ggplot(data = df_biel_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
  # lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_biel_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_biel_resp_div$Med, lty = 2) +
  geom_line()
  # lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_biel_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_biel_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_biel_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_biel_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_biel_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_biel_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
  # lims(y = c(smin, smax))

plot_lake_biel <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Biel')

plot_lake_biel

ggsave(filename = "plot_lake_biel.pdf", plot = plot_lake_biel, width = 7, height = 7)
```

#### Brienz

```{r}

df_brienz_pred <- readRDS("df_predictions/df_pred_Brienz.rds")
df_brienz_pred_pres <- readRDS("df_predictions_presence/df_pred_Brienz.rds")
df_brienz_deriv <- readRDS("df_derivatives/df_deriv_Brienz.rds")
df_brienz_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Brienz.rds")
df_brienz_resp_div <- readRDS("df_response_diversity/df_resp_div_Brienz.rds")
df_brienz_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Brienz.rds")

##plotting test brienz
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_brienz_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
  # lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_brienz_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
  # lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_brienz_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_brienz_resp_div$Med, lty = 2) +
  geom_line()
  # lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_brienz_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_brienz_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_brienz_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_brienz_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_brienz_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_brienz_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
  # lims(y = c(smin, smax))

plot_lake_brienz <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Brienz')

plot_lake_brienz

ggsave(filename = "plot_lake_brienz.pdf", plot = plot_lake_brienz, width = 7, height = 7)
```

#### Constance

```{r}
df_constance_pred <- readRDS("df_predictions/df_pred_Constance.rds")
df_constance_pred_pres <- readRDS("df_predictions_presence/df_pred_Constance.rds")
df_constance_deriv <- readRDS("df_derivatives/df_deriv_Constance.rds")
df_constance_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Constance.rds")
df_constance_resp_div <- readRDS("df_response_diversity/df_resp_div_Constance.rds")
df_constance_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Constance.rds")

##plotting test constance
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_constance_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_constance_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_constance_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_constance_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_constance_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_constance_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_constance_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_constance_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_constance_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_constance_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_constance <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Constance')

plot_lake_constance

ggsave(filename = "plot_lake_constance.pdf", plot = plot_lake_constance, width = 7, height = 7)
```

#### Geneva

```{r}
df_geneva_pred <- readRDS("df_predictions/df_pred_Geneva.rds")
df_geneva_pred_pres <- readRDS("df_predictions_presence/df_pred_Geneva.rds")
df_geneva_deriv <- readRDS("df_derivatives/df_deriv_Geneva.rds")
df_geneva_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Geneva.rds")
df_geneva_resp_div <- readRDS("df_response_diversity/df_resp_div_Geneva.rds")
df_geneva_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Geneva.rds")

##plotting test geneva
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_geneva_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_geneva_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_geneva_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_geneva_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_geneva_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_geneva_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_geneva_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_geneva_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_geneva_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_geneva_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_geneva <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Geneva')

plot_lake_geneva

ggsave(filename = "plot_lake_geneva.pdf", plot = plot_lake_geneva, width = 7, height = 7)

```

#### Joux

```{r}
df_joux_pred <- readRDS("df_predictions/df_pred_Joux.rds")
df_joux_pred_pres <- readRDS("df_predictions_presence/df_pred_Joux.rds")
df_joux_deriv <- readRDS("df_derivatives/df_deriv_Joux.rds")
df_joux_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Joux.rds")
df_joux_resp_div <- readRDS("df_response_diversity/df_resp_div_Joux.rds")
df_joux_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Joux.rds")

##plotting test joux
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_joux_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_joux_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_joux_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_joux_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_joux_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_joux_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_joux_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_joux_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_joux_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_joux_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_joux <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Joux')

plot_lake_joux

ggsave(filename = "plot_lake_joux.pdf", plot = plot_lake_joux, width = 7, height = 7)
```

#### Lucerne

```{r}
df_lucerne_pred <- readRDS("df_predictions/df_pred_Lucerne.rds")
df_lucerne_pred_pres <- readRDS("df_predictions_presence/df_pred_Lucerne.rds")
df_lucerne_deriv <- readRDS("df_derivatives/df_deriv_Lucerne.rds")
df_lucerne_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Lucerne.rds")
df_lucerne_resp_div <- readRDS("df_response_diversity/df_resp_div_Lucerne.rds")
df_lucerne_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Lucerne.rds")

##plotting test lucerne
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_lucerne_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_lucerne_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_lucerne_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_lucerne_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_lucerne_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_lucerne_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_lucerne_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_lucerne_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_lucerne_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_lucerne_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_lucerne <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Lucerne')

plot_lake_lucerne

ggsave(filename = "plot_lake_lucerne.pdf", plot = plot_lake_lucerne, width = 7, height = 7)
```

#### Lugano

```{r}
df_lugano_pred <- readRDS("df_predictions/df_pred_Lugano.rds")
df_lugano_pred_pres <- readRDS("df_predictions_presence/df_pred_Lugano.rds")
df_lugano_deriv <- readRDS("df_derivatives/df_deriv_Lugano.rds")
df_lugano_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Lugano.rds")
df_lugano_resp_div <- readRDS("df_response_diversity/df_resp_div_Lugano.rds")
df_lugano_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Lugano.rds")

##plotting test lugano
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_lugano_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_lugano_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_lugano_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_lugano_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_lugano_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_lugano_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_lugano_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_lugano_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_lugano_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_lugano_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_lugano <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Lugano')

plot_lake_lugano

ggsave(filename = "plot_lake_lugano.pdf", plot = plot_lake_lugano, width = 7, height = 7)
```

#### Maggiore

```{r}
df_maggiore_pred <- readRDS("df_predictions/df_pred_Maggiore.rds")
df_maggiore_pred_pres <- readRDS("df_predictions_presence/df_pred_Maggiore.rds")
df_maggiore_deriv <- readRDS("df_derivatives/df_deriv_Maggiore.rds")
df_maggiore_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Maggiore.rds")
df_maggiore_resp_div <- readRDS("df_response_diversity/df_resp_div_Maggiore.rds")
df_maggiore_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Maggiore.rds")

##plotting test maggiore
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_maggiore_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_maggiore_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_maggiore_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_maggiore_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_maggiore_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_maggiore_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_maggiore_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_maggiore_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_maggiore_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_maggiore_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_maggiore <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Maggiore')

plot_lake_maggiore

ggsave(filename = "plot_lake_maggiore.pdf", plot = plot_lake_maggiore, width = 7, height = 7)
```

#### Morat

```{r}
df_morat_pred <- readRDS("df_predictions/df_pred_Morat.rds")
df_morat_pred_pres <- readRDS("df_predictions_presence/df_pred_Morat.rds")
df_morat_deriv <- readRDS("df_derivatives/df_deriv_Morat.rds")
df_morat_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Morat.rds")
df_morat_resp_div <- readRDS("df_response_diversity/df_resp_div_Morat.rds")
df_morat_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Morat.rds")

##plotting test morat
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_morat_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_morat_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_morat_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_morat_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_morat_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_morat_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_morat_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_morat_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_morat_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_morat_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_morat <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Morat')

plot_lake_morat

ggsave(filename = "plot_lake_morat.pdf", plot = plot_lake_morat, width = 7, height = 7)
```

#### Neuchatel

```{r}
df_neuchatel_pred <- readRDS("df_predictions/df_pred_Neuchatel.rds")
df_neuchatel_pred_pres <- readRDS("df_predictions_presence/df_pred_Neuchatel.rds")
df_neuchatel_deriv <- readRDS("df_derivatives/df_deriv_Neuchatel.rds")
df_neuchatel_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Neuchatel.rds")
df_neuchatel_resp_div <- readRDS("df_response_diversity/df_resp_div_Neuchatel.rds")
df_neuchatel_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Neuchatel.rds")

##plotting test neuchatel
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_neuchatel_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_neuchatel_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_neuchatel_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_neuchatel_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_neuchatel_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_neuchatel_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_neuchatel_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_neuchatel_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_neuchatel_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_neuchatel_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_neuchatel <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Neuchatel')

plot_lake_neuchatel

ggsave(filename = "plot_lake_neuchatel.pdf", plot = plot_lake_neuchatel, width = 7, height = 7)
```

#### Poschiavo

```{r}
df_poschiavo_pred <- readRDS("df_predictions/df_pred_Poschiavo.rds")
df_poschiavo_pred_pres <- readRDS("df_predictions_presence/df_pred_Poschiavo.rds")
df_poschiavo_deriv <- readRDS("df_derivatives/df_deriv_Poschiavo.rds")
df_poschiavo_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Poschiavo.rds")
df_poschiavo_resp_div <- readRDS("df_response_diversity/df_resp_div_Poschiavo.rds")
df_poschiavo_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Poschiavo.rds")

##plotting test poschiavo
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_poschiavo_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_poschiavo_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_poschiavo_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_poschiavo_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_poschiavo_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_poschiavo_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_poschiavo_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_poschiavo_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_poschiavo_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_poschiavo_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_poschiavo <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Poschiavo')

plot_lake_poschiavo

ggsave(filename = "plot_lake_poschiavo.pdf", plot = plot_lake_poschiavo, width = 7, height = 7)
```

#### Sarnen

```{r}
df_sarnen_pred <- readRDS("df_predictions/df_pred_Sarnen.rds")
df_sarnen_pred_pres <- readRDS("df_predictions_presence/df_pred_Sarnen.rds")
df_sarnen_deriv <- readRDS("df_derivatives/df_deriv_Sarnen.rds")
df_sarnen_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Sarnen.rds")
df_sarnen_resp_div <- readRDS("df_response_diversity/df_resp_div_Sarnen.rds")
df_sarnen_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Sarnen.rds")

##plotting test sarnen
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_sarnen_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_sarnen_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_sarnen_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_sarnen_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_sarnen_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_sarnen_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_sarnen_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_sarnen_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_sarnen_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_sarnen_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_sarnen <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Sarnen')

plot_lake_sarnen


ggsave(filename = "plot_lake_sarnen.pdf", plot = plot_lake_sarnen, width = 7, height = 7)

```

#### Thun

```{r}
df_thun_pred <- readRDS("df_predictions/df_pred_Thun.rds")
df_thun_pred_pres <- readRDS("df_predictions_presence/df_pred_Thun.rds")
df_thun_deriv <- readRDS("df_derivatives/df_deriv_Thun.rds")
df_thun_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Thun.rds")
df_thun_resp_div <- readRDS("df_response_diversity/df_resp_div_Thun.rds")
df_thun_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Thun.rds")

##plotting test thun
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_thun_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_thun_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_thun_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_thun_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_thun_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_thun_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_thun_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_thun_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_thun_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_thun_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_thun <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Thun')

plot_lake_thun

ggsave(filename = "plot_lake_thun.pdf", plot = plot_lake_thun, width = 7, height = 7)

```

#### Walen

```{r}
df_walen_pred <- readRDS("df_predictions/df_pred_Walen.rds")
df_walen_pred_pres <- readRDS("df_predictions_presence/df_pred_Walen.rds")
df_walen_deriv <- readRDS("df_derivatives/df_deriv_Walen.rds")
df_walen_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Walen.rds")
df_walen_resp_div <- readRDS("df_response_diversity/df_resp_div_Walen.rds")
df_walen_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Walen.rds")

##plotting test walen
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_walen_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_walen_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_walen_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_walen_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_walen_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_walen_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_walen_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_walen_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_walen_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_walen_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_walen <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Walen')

plot_lake_walen

ggsave(filename = "plot_lake_walen.pdf", plot = plot_lake_walen, width = 7, height = 7)
```

#### Zug

```{r}
df_zug_pred <- readRDS("df_predictions/df_pred_Zug.rds")
df_zug_pred_pres <- readRDS("df_predictions_presence/df_pred_Zug.rds")
df_zug_deriv <- readRDS("df_derivatives/df_deriv_Zug.rds")
df_zug_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Zug.rds")
df_zug_resp_div <- readRDS("df_response_diversity/df_resp_div_Zug.rds")
df_zug_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Zug.rds")

##plotting test zug
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_zug_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_zug_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_zug_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_zug_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_zug_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_zug_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_zug_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_zug_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_zug_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_zug_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_zug <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Zug')

plot_lake_zug

ggsave(filename = "plot_lake_zug.pdf", plot = plot_lake_zug, width = 7, height = 7)
```

#### Zurich

```{r}
df_zurich_pred <- readRDS("df_predictions/df_pred_Zurich.rds")
df_zurich_pred_pres <- readRDS("df_predictions_presence/df_pred_Zurich.rds")
df_zurich_deriv <- readRDS("df_derivatives/df_deriv_Zurich.rds")
df_zurich_deriv_pres <- readRDS("df_derivatives_presence/df_deriv_Zurich.rds")
df_zurich_resp_div <- readRDS("df_response_diversity/df_resp_div_Zurich.rds")
df_zurich_resp_div_pres <- readRDS("df_response_diversity_presence/df_resp_div_Zurich.rds")

##plotting test zurich
fig_a <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Abundance", tag = "a)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_zurich_pred, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(ymin_p, ymax_p))

fig_b <- ggplot(data = df_zurich_deriv, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "b)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)
# lims(y = c(dmin, dmax))


fig_c <- ggplot(data = df_zurich_resp_div, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "c)") +
  geom_hline(yintercept = df_zurich_resp_div$Med, lty = 2) +
  geom_line()
# lims(y = c(rmin_p, rmax_p))

fig_d <- ggplot(data = df_zurich_resp_div, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "d)") +
  geom_line()


fig_e <- ggplot() +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Presence", tag = "e)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(data = df_zurich_pred_pres, mapping = aes(x = temp, y = model_prediction, color = Species), show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_f <- ggplot(data = df_zurich_deriv_pres, mapping = aes(x = temp, y = derivative, color = Species)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Derivative", tag = "f)") +
  geom_hline(
    yintercept = 0,
    lty = 2) +
  geom_line(show.legend = FALSE) +
  scale_colour_manual(values = lakeColors, guide = NULL)



fig_g <- ggplot(data = df_zurich_resp_div_pres, mapping = aes(x = temp, y = rdiv)) +
  theme_classic(base_size = 14) +
  labs(x = NULL, y = "Dissimilarity", tag = "g)") +
  geom_hline(yintercept = df_zurich_resp_div$Med, lty = 2) +
  geom_line()


fig_h <- ggplot(data = df_zurich_resp_div_pres, mapping = aes(x = temp, y = sign)) +
  theme_classic(base_size = 14) +
  labs(x = "Temperature", y = "Sign", tag = "h)") +
  geom_line()
# lims(y = c(smin, smax))

plot_lake_zurich <- fig_a + fig_b + fig_c + fig_d + fig_e + fig_f + fig_g + fig_h +plot_layout(nrow = 4, byrow = FALSE) +   plot_annotation(title = 'Response diversity in Lake Zurich')

plot_lake_zurich

ggsave(filename = "plot_lake_zurich.pdf", plot = plot_lake_zurich, width = 7, height = 7)
```
